---
title: "WheatResistance2012-2015"
author: "Nicolas O. Rode"
date: "Aug, 18th 2016"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: true
---

# Set working directory
```{r}
setwd("/homedir/rode/Rstudio/Yan/2012-2015/18082016")
list.files()
## Load Packages
##see: http://stats.stackexchange.com/questions/18709/lme4-or-other-open-source-r-package-code-equivalent-to-asreml-r
library(asreml)
library(asremlPlus)
library(lattice)
source("~/Rstudio/Rsrc/pin.R")
source("~/Rstudio/Rsrc/AIC_table_function.R")

data <- read.table("~/Rstudio/Yan/2012-2015/18082016/Data2012_2015.csv" , header=T , sep="," , na.strings="NA")
head(data)
```
# Format variables
```{r}
## 1529 rows
nrow(data)

## 423 rows with missing data
nrow(data[is.na(data$NV)|is.na(data$Elisa)|is.na(data$genotype),])

## 209 missing genotypes
sum(is.na(data$genotype))
## 380 missing visual scores
sum(is.na(data$NV))
## 416 missing Elisa
sum(is.na(data$Elisa))
## 361 missing Elisa
sum(is.na(data$QPCR[data$Year=="2015"]))

data <- data[order(data$Year,data$Y,data$X),]

## Convert position and year as factors
data$X <- as.factor(data$X)
data$Y <- as.factor(data$Y)
data$Year <- as.factor(data$Year)
data$Obs <- as.factor(1:nrow(data))
data$genotype_year <- paste(data$genotype,data$Year,sep="_")
data$pop2015 <- data$pop
data$pop2015 <- ifelse(data$Year=="2012",NA,as.character(data$pop2015))
data$pop2015 <- as.factor(data$pop2015)
data$pop2015mean <- as.factor(ifelse(data$pop2015=="pescadou","pescadou","DLDS"))

data$cross2015 <- data$cross
data$cross2015 <- ifelse(data$Year=="2012",NA,as.character(data$cross2015))
data$cross2015 <- as.factor(data$cross2015)
data$popmean <- as.factor(ifelse(data$pop=="pescadou","pescadou","DLDS"))
levels(data$popmean)

## Factors to test for indirect genetic effects
levY <- sort(unique(c(levels(data$neigh2),levels(data$neigh6))))
data$neigh2<-factor(data$neigh2,levels=levY)
data$neigh6<-factor(data$neigh6,levels=levY)
data$Year2012 <- ifelse(data$Year=="2012",1,0)
data$Year2015 <- ifelse(data$Year=="2015",1,0)
## Grid arrangement on the field plot
Neighbour <- data.frame(matrix(c("neigh1","neigh2","neigh3","neigh8","focal_genotype","neigh4","neigh7","neigh6","neigh5"),byrow=F,ncol=3))
colnames(Neighbour) <- c("Y1","Y2","Y3")
rownames(Neighbour) <- c("X1","X2","X3")
Neighbour

## Dataset for model AR1 on X
data2 <- data[order(data$Year,data$X,data$Y),]

head(data)
tail(data,n=7)

```


# Phenotypic data
```{r}
histogram(~NV|pop*Year,data=data[data$pop=="Dic2 x Lloyd"|data$pop=="Dic2 x Silur",])
histogram(~Elisa|pop*Year,data=data[data$pop=="Dic2 x Lloyd"|data$pop=="Dic2 x Silur",])
histogram(~QPCR|pop,data=data[data$pop=="Dic2 x Lloyd"|data$pop=="Dic2 x Silur",])

```

# Severity Score (NV)
## Model selection
```{r Severity Score}
## Spatially uncorrelated and correlated (AR1) environmental variance on row (X) and column (Y) , genotype and no linear X effect (model A for genetic effects and model 3 for residuals)
## By default, only 13 iterations, so increase this number with maxiter
m0 <- asreml(NV ~  popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):ar1(Y):ar1(X),random=~corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+corgh(Year):at(pop,"Dic2 x Silur"):genotype+at(Year):X_Y,na.method.X="include",data=data,maxiter=40,trace=F)
m0 <-update(m0)

hist(m0$coefficients$random[grepl("_pop_Dic2 x Lloyd",names(m0$coefficients$random))&m0$coefficient$random!=0],main="Dic2 x Lloyd",xlab=NA)
hist(m0$coefficients$random[grepl("_pop_Dic2 x Silur",names(m0$coefficients$random))&m0$coefficient$random!=0],main="Dic2 x Silur",xlab=NA)

m0$coefficients$fixed

summary(m0)$varcomp

## No genetic correlation between years (model B for genetic effects)
##- corgh(Year)->diag(Year)
m1 <- asreml(NV ~  popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):ar1(Y):ar1(X),random=~diag(Year):at(pop,"Dic2 x Lloyd"):genotype+diag(Year):at(pop,"Dic2 x Silur"):genotype+at(Year):X_Y,na.method.X="include",data=data,maxiter=50,trace=F)
m1 <-update(m1)

## No difference in genetic effects between years (model C for genetic effects)
##- corgh(Year):
m2 <- asreml(NV ~  popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):ar1(Y):ar1(X),random=~at(pop,"Dic2 x Lloyd"):genotype+at(pop,"Dic2 x Silur"):genotype+at(Year):X_Y,na.method.X="include",data=data,maxiter=40,trace=F)
m2 <-update(m2)

summary(m2)$varcomp

## Same spatially uncorrelated environmental variances, σ_uncor^2, in 2012 and 2015
## - at(Year):X_Y + Obs
m3 <- asreml(NV ~  popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):ar1(Y):ar1(X),random=~corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+corgh(Year):at(pop,"Dic2 x Silur"):genotype+Obs,na.method.X="include",data=data,maxiter=40,trace=F)
summary(m3)$varcomp

## AR1 on X only
m4 <- asreml(NV ~  popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):id(Y):ar1(X),random=~corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+corgh(Year):at(pop,"Dic2 x Silur"):genotype+at(Year):X_Y,na.method.X="include",data=data,maxiter=40,trace=F)
summary(m4)$varcomp

## AR1 on Y only
m5 <- asreml(NV ~ popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):id(X):ar1(Y),random=~corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+corgh(Year):at(pop,"Dic2 x Silur"):genotype+at(Year):X_Y,na.method.X="include",data=data2,maxiter=40,trace=F)
summary(m5)$varcomp

## No spatially correlated environmental variance (model 1 for residuals)
m6 <- asreml(NV ~  popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):id(Y):id(X),random=~corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+corgh(Year):at(pop,"Dic2 x Silur"):genotype,na.method.X="include",data=data,maxiter=40,trace=F)

summary(m6)$varcomp

## No spatially uncorrelated environmental variance (model 2 for residuals)
m7 <- asreml(NV ~ popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):ar1(Y):ar1(X),random=~corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+corgh(Year):at(pop,"Dic2 x Silur"):genotype,na.method.X="include",data=data,maxiter=40,trace=F)


AICcASRemlRmd(paste("m",0:7,sep=""))
filename<-paste('AICcTable_ASReml-R_Analyses_', Sys.Date(),".csv",sep="")
file.rename(from=filename, to=paste('AICcTable_ASReml-R_Analyses_', Sys.Date(),"NV",".csv",sep=""))

summary(m0)$varcomp

## Goodness of fit
plot(m0)
plot.asrVariogram(variogram(m0))

## Spatially correlated residuals
hist(m0$residuals,main="Autocorrelated residual distribution")
## Spatially uncorrelated residuals
hist(m0$coefficient$random[grepl("X_Y",names(m0$coefficient$random))&m0$coefficient$random!=0],main="Non-autocorrelated residual  distribution")


## Check spatial auto-correlation

## 2012
y <- -100:100*0.1
plot(y,summary(m0)$varcomp[10,2]^abs(y))
x <- -10:10*2
plot(x,summary(m0)$varcomp[11,2]^abs(x))
## 2015
y <- -100:100*0.1
plot(y,summary(m0)$varcomp[13,2]^abs(y))
x <- -10:10*2
plot(x,summary(m0)$varcomp[14,2]^abs(x))
```

## Fixed effects for severity score (NV)
```{r}
## Fixed effects
m0 <- asreml(NV ~  popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):ar1(Y):ar1(X),random=~corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+corgh(Year):at(pop,"Dic2 x Silur"):genotype+at(Year):X_Y,na.method.X="include",data=data,maxiter=40,trace=F)

m0$coefficients$fixed

##Conditional Wald F-test to test factors and their interaction
wald.asreml(m0, ssType="conditional", denDF="numeric")

##Predictions for the interaction
pred <- predict(m0,classify="popmean:Year",sed=list("popmean:Year"=T))
pred$predictions

## Covariance between estimates
svc(m0)

```


## Compute genetic correlation for severity score (NV)
```{r}
m0 <- asreml(NV ~ -1+popmean:Year,rcov=~at(Year):ar1(Y):ar1(X),random=~corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+corgh(Year):at(pop,"Dic2 x Silur"):genotype+at(Year):X_Y,na.method.X="include",data=data,maxiter=40,trace=F)

summary(m0)$varcomp[c(1,4),2:3]

```
## Compute heritabilities for NV
```{r}

## Heritability Dic2 x Lloyd 2012
summary(m0)$varcomp[2,2]/sum(summary(m0)$varcomp[c(2,7),2])
Heritability <- as.numeric(pin(m0,prop~(V2)/(V2+V7)))
CI<-c(Heritability[1]-qnorm(0.975)* Heritability[2], Heritability[1]+qnorm(0.975)* Heritability[2])
names(CI) <- c("Lower95%CI","Upper95%CI")
CI

## Heritability Dic2 x Lloyd 2015
summary(m0)$varcomp[3,2]/sum(summary(m0)$varcomp[c(3,8),2])
Heritability <- as.numeric(pin(m0,prop~(V3)/(V3+V8)))
CI<-c(Heritability[1]-qnorm(0.975)* Heritability[2], Heritability[1]+qnorm(0.975)* Heritability[2])
names(CI) <- c("Lower95%CI","Upper95%CI")
CI

## Heritability Dic2 x Silur 2012
summary(m0)$varcomp[5,2]/sum(summary(m0)$varcomp[c(5,7),2])
Heritability <- as.numeric(pin(m0,prop~(V5)/(V5+V7)))
CI<-c(Heritability[1]-qnorm(0.975)* Heritability[2], Heritability[1]+qnorm(0.975)* Heritability[2])
names(CI) <- c("Lower95%CI","Upper95%CI")
CI

## Heritability Dic2 x Silur 2015
summary(m0)$varcomp[6,2]/sum(summary(m0)$varcomp[c(6,8),2])
Heritability <- as.numeric(pin(m0,prop~(V6)/(V6+V8)))
CI<-c(Heritability[1]-qnorm(0.975)* Heritability[2], Heritability[1]+qnorm(0.975)* Heritability[2])
names(CI) <- c("Lower95%CI","Upper95%CI")
CI

```

## Proportion of total variance explained by spatial autocorrelation for NV
```{r}

## Spatially correlated variance Dic2 x Lloyd 2012
summary(m0)$varcomp[9,2]/sum(summary(m0)$varcomp[c(2,7,9),2])
## Spatial autocorrelation Dic2 x Silur 2012
summary(m0)$varcomp[9,2]/sum(summary(m0)$varcomp[c(5,7,9),2])

## Spatially correlated variance Dic2 x Lloyd 2015
summary(m0)$varcomp[12,2]/sum(summary(m0)$varcomp[c(3,8,12),2])
## Spatial autocorrelation  Dic2 x Silur 2015
summary(m0)$varcomp[12,2]/sum(summary(m0)$varcomp[c(6,8,12),2])
```

## Extract BLUPs for NV
```{r}
hist(m0$coefficient$random[grepl("genotype",names(m0$coefficient$random))&m0$coefficient$random!=0],main="BLUP distribution")

## 357 genotypes in total
length(unique(data$genotype[data$cross=="cross"&!is.na(data$cross)&!is.na(data$NV)]))

## 10 genotypes without replication
tab <- table(data$genotype[data$cross=="cross"&!is.na(data$cross)&!is.na(data$NV)])
length(tab[tab==1])

## Extract BLUPS
coefNV <- m0$coefficient$random[grepl("genotype",names(m0$coefficient$random))&m0$coefficient$random!=0]
## Extract genotype, pop, year
coefNVname <- strsplit(names(coefNV),":")
coefNVname <- lapply(coefNVname,function(x){strsplit(x,"_")})

year = do.call("rbind", lapply(coefNVname, "[[", 1))
pop = do.call("rbind", lapply(coefNVname, "[[", 2))
geno = do.call("rbind", lapply(coefNVname, "[[", 3))

coefNV <- data.frame(pop[,3],geno[,2],year[,2],coefNV)

names(coefNV) <- c("pop","geno","year","BLUP")
head(coefNV)

## 357 genotypes
nrow(coefNV[coefNV$year=="2012",])
nrow(coefNV[coefNV$year=="2015",])

coefNV$genotype_year <- paste(coefNV$geno,coefNV$year,sep="_")

coefNV$real <- coefNV$genotype_year%in%data$genotype_year
head(coefNV[coefNV$real==FALSE,])
## Get rid of genotypes with infered BLUPS (i.e. that were not observed that year)
coefNV <- coefNV[coefNV$real==T,]
write.csv(coefNV,file="BLUPsNV2012_2015.csv",row.names=F,quote=F)

```

# ELISA
## Model selection
```{r ELISA}

## Spatially uncorrelated and correlated (AR1) environmental variance on row (X) and column (Y) , genotype and no linear X effect (model A for direct genetic effects and model 3 for residuals) (not converged)
## By default, only 13 iterations, so increase this number with maxiter (not converged)
m0 <- asreml(Elisa ~ popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):ar1(Y):ar1(X),random=~corgh(Year):at(pop,"Dic2 x Silur"):genotype+corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+at(Year):X_Y,na.method.X="include",data=data,maxiter=100,trace=F)

hist(m0$coefficients$random[grepl("_pop_Dic2 x Lloyd",names(m0$coefficients$random))&m0$coefficient$random!=0],main="Dic2 x Lloyd",xlab=NA)
hist(m0$coefficients$random[grepl("_pop_Dic2 x Silur",names(m0$coefficients$random))&m0$coefficient$random!=0],main="Dic2 x Silur",xlab=NA)

summary(m0)$varcomp

## No genetic correlation between years (model B for genetic effects)
##- corgh(Year)->diag(Year)
m1 <- asreml(Elisa ~ popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):ar1(Y):ar1(X),random=~diag(Year):at(pop,"Dic2 x Lloyd"):genotype+diag(Year):at(pop,"Dic2 x Silur"):genotype+at(Year):X_Y,na.method.X="include",data=data,maxiter=50,trace=F)

## No difference in genetic effects between years (model C for genetic effects)
##- corgh(Year):
m2 <- asreml(Elisa ~ popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):ar1(Y):ar1(X),random=~at(pop,"Dic2 x Lloyd"):genotype+at(pop,"Dic2 x Silur"):genotype+at(Year):X_Y,na.method.X="include",data=data,maxiter=40,trace=F)
summary(m2)$varcomp

## Same spatially uncorrelated environmental variances, σ_uncor^2, in 2012 and 2015
## - at(Year):X_Y + Obs
m3 <- asreml(Elisa ~ popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):ar1(Y):ar1(X),random=~corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+corgh(Year):at(pop,"Dic2 x Silur"):genotype+Obs,na.method.X="include",data=data,maxiter=40,trace=F)
summary(m3)$varcomp

##AR1 on X only
m4 <- asreml(Elisa ~ popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):id(Y):ar1(X),random=~corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+corgh(Year):at(pop,"Dic2 x Silur"):genotype+at(Year):X_Y,na.method.X="include",data=data,maxiter=40,trace=F)
m4 <- update(m4)
summary(m4)$varcomp

##AR1 on Y only
m5 <- asreml(Elisa ~ popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):id(X):ar1(Y),random=~corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+corgh(Year):at(pop,"Dic2 x Silur"):genotype+at(Year):X_Y,na.method.X="include",data=data2,maxiter=40,trace=F)
summary(m5)$varcomp

## No spatially correlated environmental variance (model 1 for residuals)
m6 <- asreml(Elisa ~ popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):id(Y):id(X),random=~corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+corgh(Year):at(pop,"Dic2 x Silur"):genotype,na.method.X="include",data=data,maxiter=40,trace=F)

summary(m6)$varcomp

## No spatially uncorrelated environmental variance (model 2 for residuals)
m7 <- asreml(Elisa ~ popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):ar1(Y):ar1(X),random=~corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+corgh(Year):at(pop,"Dic2 x Silur"):genotype,na.method.X="include",data=data,maxiter=40,trace=F)

AICcASRemlRmd(paste("m",0:7,sep=""))
filename<-paste('AICcTable_ASReml-R_Analyses_', Sys.Date(),".csv",sep="")
file.rename(from=filename, to=paste('AICcTable_ASReml-R_Analyses_', Sys.Date(),"Elisa",".csv",sep=""))


summary(m0)$varcomp

## Goodness of fit
plot(m0)
plot.asrVariogram(variogram(m0))
hist(m0$residuals,main="Autocorrelated residual distribution")
hist(m0$coefficient$random[grepl("X_Y",names(m0$coefficient$random))&m0$coefficient$random!=0],main="Non-autocorrelated residual  distribution")


## Check spatial auto-correlation
y <- -100:100*0.1
plot(y,summary(m0)$varcomp[10,2]^abs(y))
x <- -10:10*2
plot(x,summary(m0)$varcomp[11,2]^abs(x))

y <- -100:100*0.1
plot(y,summary(m0)$varcomp[13,2]^abs(y))
x <- -10:10*2
plot(x,summary(m0)$varcomp[14,2]^abs(x))
```

## Fixed effects for Elisa
```{r}
## Fixed effects
m0 <- asreml(Elisa ~ popmean+Year+popmean:Year+pol(X,-1)+pol(Y,-1),rcov=~at(Year):ar1(Y):ar1(X),random=~corgh(Year):at(pop,"Dic2 x Silur"):genotype+corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+at(Year):X_Y,na.method.X="include",data=data,maxiter=100,trace=F)


m0$coefficients$fixed

##Conditional Wald F-test to test factors and their interaction
wald.asreml(m0, ssType="conditional", denDF="numeric")

##Predictions for the interaction
pred <- predict(m0,classify="popmean:Year",sed=list("popmean:Year"=T))
pred$predictions

## Covariance between estimates
svc(m0)

```

## Compute genetic correlation for Elisa
```{r}
m0 <- asreml(Elisa ~ -1+popmean,rcov=~at(Year):ar1(Y):ar1(X),random=~corgh(Year):at(pop,"Dic2 x Lloyd"):genotype+corgh(Year):at(pop,"Dic2 x Silur"):genotype+at(Year):X_Y,na.method.X="include",data=data,maxiter=40,trace=F)
m0 <- update(m0)
m0 <- update(m0)

summary(m0)$varcomp[c(1,4),2:3]
```

## Compute heritabilities for Elisa
```{r}
## Heritability Dic2 x Lloyd 2012
summary(m0)$varcomp[2,2]/sum(summary(m0)$varcomp[c(2,7),2])
Heritability <- as.numeric(pin(m0,prop~(V2)/(V2+V7)))
CI<-c(Heritability[1]-qnorm(0.975)* Heritability[2], Heritability[1]+qnorm(0.975)* Heritability[2])
names(CI) <- c("Lower95%CI","Upper95%CI")
CI

## Heritability Dic2 x Lloyd 2015
summary(m0)$varcomp[3,2]/sum(summary(m0)$varcomp[c(3,8),2])
Heritability <- as.numeric(pin(m0,prop~(V3)/(V3+V8)))
CI<-c(Heritability[1]-qnorm(0.975)* Heritability[2], Heritability[1]+qnorm(0.975)* Heritability[2])
names(CI) <- c("Lower95%CI","Upper95%CI")
CI

## Heritability Dic2 x Silur 2012
summary(m0)$varcomp[5,2]/sum(summary(m0)$varcomp[c(5,7),2])

Heritability <- as.numeric(pin(m0,prop~(V5)/(V5+V7)))
CI<-c(Heritability[1]-qnorm(0.975)* Heritability[2], Heritability[1]+qnorm(0.975)* Heritability[2])
names(CI) <- c("Lower95%CI","Upper95%CI")
CI

## Heritability Dic2 x Silur 2015
summary(m0)$varcomp[6,2]/sum(summary(m0)$varcomp[c(6,8),2])

Heritability <- as.numeric(pin(m0,prop~(V6)/(V6+V8)))
CI<-c(Heritability[1]-qnorm(0.975)* Heritability[2], Heritability[1]+qnorm(0.975)* Heritability[2])
names(CI) <- c("Lower95%CI","Upper95%CI")
CI

```
## Proportion of total variance explained by spatial autocorrelation for Elisa
```{r}

## Spatial autocorrelation Dic2 x Lloyd 2012
summary(m0)$varcomp[9,2]/sum(summary(m0)$varcomp[c(2,7,9),2])
## Spatial autocorrelation Dic2 x Silur 2012
summary(m0)$varcomp[9,2]/sum(summary(m0)$varcomp[c(5,7,9),2])

## Spatial autocorrelation Dic2 x Lloyd 2012
summary(m0)$varcomp[12,2]/sum(summary(m0)$varcomp[c(3,8,12),2])

## Spatial autocorrelation  Dic2 x Silur 2015
summary(m0)$varcomp[12,2]/sum(summary(m0)$varcomp[c(6,8,12),2])
```
## Extract BLUPs
```{r}
hist(m0$coefficient$random[grepl("genotype",names(m0$coefficient$random))&m0$coefficient$random!=0],main="BLUP distribution")

## 357 genotypes in total
length(unique(data$genotype[data$cross=="cross"&!is.na(data$cross)&!is.na(data$Elisa)]))

## 15 genotypes without replication
tab <- table(data$genotype[data$cross=="cross"&!is.na(data$cross)&!is.na(data$Elisa)])
length(tab[tab==1])

## Extract BLUPS
coefElisa <- m0$coefficient$random[grepl("genotype",names(m0$coefficient$random))&m0$coefficient$random!=0]
## Extract genotype, pop, year
coefElisaname <- strsplit(names(coefElisa),":")
coefElisaname <- lapply(coefElisaname,function(x){strsplit(x,"_")})

year = do.call("rbind", lapply(coefElisaname, "[[", 1))
pop = do.call("rbind", lapply(coefElisaname, "[[", 2))
geno = do.call("rbind", lapply(coefElisaname, "[[", 3))

BLUPElisa <- data.frame(pop[,3],geno[,2],year[,2],coefElisa)

names(BLUPElisa) <- c("pop","geno","year","BLUP")
head(BLUPElisa)

## 357 genotypes
nrow(BLUPElisa[BLUPElisa$year=="2012",])
nrow(BLUPElisa[BLUPElisa$year=="2015",])

BLUPElisa$genotype_year <- paste(BLUPElisa$geno,BLUPElisa$year,sep="_")

BLUPElisa$real <- BLUPElisa$genotype_year%in%data$genotype_year
head(BLUPElisa[BLUPElisa$real==FALSE,])

## Example of an unreplicated genotype
data[data$genotype=="BX07.2.1f1.17.1"&!is.na(data$genotype),]
BLUPElisa[BLUPElisa$geno=="BX07.2.1f1.17.1"&!is.na(BLUPElisa$geno),]

## Get rid of genotypes with infered BLUPS (i.e. that were not observed that year)
BLUPElisa <- BLUPElisa[BLUPElisa$real==T,]

write.csv(BLUPElisa,file="BLUPsElisa2012_2015.csv",row.names=F,quote=F)

```


# qPCR
## Model selection
```{r qPCR}
data2015 <- data[data$Year=="2015",]
## Spatially uncorrelated and correlated (AR1) environmental variance on row (X) and column (Y) , genotype and no linear X effect (model A for direct genetic effects and model 3 for residuals) (not converged)
## By default, only 13 iterations, so increase this number with maxiter
m0 <- asreml(QPCR ~ -1+pop2015mean+pol(X,-1)+pol(Y,-1),rcov=~ar1(Y):ar1(X),random=~at(pop2015,"Dic2 x Lloyd"):genotype+at(pop2015,"Dic2 x Silur"):genotype+X_Y,na.method.X="include",data=data2015,maxiter=40,trace=F)
summary(m0)$varcomp

## Distribution of breeding values for DL
hist(m0$coefficients$random[grepl("_pop2015_Dic2 x Lloyd",names(m0$coefficients$random))&m0$coefficient$random!=0],main="Dic2 x Lloyd",xlab=NA)
## Distribution of breeding values for DS
hist(m0$coefficients$random[grepl("_pop2015_Dic2 x Silur",names(m0$coefficients$random))&m0$coefficient$random!=0],main="Dic2 x Silur",xlab=NA)

##  No spatially correlated environmental variance (model 1 for residuals)
m1 <- asreml(QPCR ~ -1+pop2015mean+pol(X,-1)+pol(Y,-1),rcov=~id(Y):id(X),random=~at(pop2015,"Dic2 x Lloyd"):genotype+at(pop2015,"Dic2 x Silur"):genotype,na.method.X="include",data=data2015,maxiter=40,trace=F)
summary(m1)$varcomp

## No spatially uncorrelated environmental variance (model 2 for residuals)
m2 <- asreml(QPCR ~ -1+pop2015mean+pol(X,-1)+pol(Y,-1),rcov=~ar1(Y):ar1(X),random=~at(pop2015,"Dic2 x Lloyd"):genotype+at(pop2015,"Dic2 x Silur"):genotype,na.method.X="include",data=data2015,maxiter=40,trace=F)

##AR1 on X only
m3 <- asreml(QPCR ~ -1+pop2015mean+pol(X,-1)+pol(Y,-1),rcov=~id(Y):ar1(X),random=~at(pop2015,"Dic2 x Lloyd"):genotype+at(pop2015,"Dic2 x Silur"):genotype+X_Y,na.method.X="include",data=data2015,maxiter=40,trace=F)
summary(m3)$varcomp

##AR1 on Y only
m4 <- asreml(QPCR ~ -1+pop2015mean+pol(X,-1)+pol(Y,-1),rcov=~id(X):ar1(Y),random=~at(pop2015,"Dic2 x Lloyd"):genotype+at(pop2015,"Dic2 x Silur"):genotype+X_Y,na.method.X="include",data=data2[data2$Year=="2015",],maxiter=40,trace=F)
summary(m4)$varcomp


AICcASRemlRmd(paste("m",0:4,sep=""))
filename<-paste('AICcTable_ASReml-R_Analyses_', Sys.Date(),".csv",sep="")
file.rename(from=filename, to=paste('AICcTable_ASReml-R_Analyses_', Sys.Date(),"qPCR",".csv",sep=""))


#plot.asrVariogram(variogram(m0))
hist(m0$residuals,main="Autocorrelated residual distribution")
hist(m0$coefficient$random[grep("X_Y",names(m0$coefficient$random))],main="Non-autocorrelated residual  distribution")


## Check spatial auto-correlation
y <- -100:100*0.1
plot(y,summary(m0)$varcomp[5,2]^abs(y))
x <- -10:10*2
plot(x,summary(m0)$varcomp[6,2]^abs(x))
```
## Fixed effects for qPCR
```{r}
## Fixed effects
m1 <- asreml(QPCR ~ 1+pop2015mean+pol(X,-1)+pol(Y,-1),rcov=~id(Y):id(X),random=~at(pop2015,"Dic2 x Lloyd"):genotype+at(pop2015,"Dic2 x Silur"):genotype,na.method.X="include",data=data2015,maxiter=40,trace=F)

##Conditional Wald F-test to test factors and their interaction
wald.asreml(m1, ssType="conditional", denDF="numeric")

##Predictions for the interaction
pred <- predict(m1,classify="pop2015mean",sed=list("pop2015mean"=T))
pred$predictions

## Covariance between estimates
svc(m1)

```

## Model with lowest AICc
```{r}
m1 <- asreml(QPCR ~ -1+pop2015mean,rcov=~id(Y):id(X),random=~at(pop2015,"Dic2 x Lloyd"):genotype+at(pop2015,"Dic2 x Silur"):genotype,na.method.X="include",data=data[data$Year=="2015",],maxiter=40,trace=F)
summary(m1)$varcomp

summary(m1)$varcomp[,2:3]

```

## Compute heritabilities for qPCR
```{r}
## Heritability Dic2 x Lloyd 2012
summary(m1)$varcomp[1,2]/sum(summary(m1)$varcomp[c(1,3),2])
Heritability <- as.numeric(pin(m1,prop~(V1)/(V1+V3)))
CI<-c(Heritability[1]-qnorm(0.975)* Heritability[2], Heritability[1]+qnorm(0.975)* Heritability[2])
names(CI) <- c("Lower95%CI","Upper95%CI")
CI
## Heritability Dic2 x Silur 2012
summary(m1)$varcomp[2,2]/sum(summary(m1)$varcomp[c(2,3),2])
Heritability <- as.numeric(pin(m1,prop~(V2)/(V2+V3)))
CI<-c(Heritability[1]-qnorm(0.975)* Heritability[2], Heritability[1]+qnorm(0.975)* Heritability[2])
names(CI) <- c("Lower95%CI","Upper95%CI")
CI


```


### Spatial autocorrelation for qPCR (second best model)
```{r}
## Spatial autocorrelation Dic2 x Lloyd 2012
summary(m0)$varcomp[4,2]/sum(summary(m0)$varcomp[c(1,3,4),2])
## Spatial autocorrelation Dic2 x Silur 2012
summary(m0)$varcomp[4,2]/sum(summary(m0)$varcomp[c(2,3,4),2])

```
## Extract BLUPs
```{r}
hist(m1$coefficient$random[grepl("genotype",names(m1$coefficient$random))&m1$coefficient$random!=0],main="BLUP distribution")

## 344 genotypes in total
length(unique(data$genotype[data$cross2015=="cross"&!is.na(data$cross2015)&!is.na(data$QPCR)]))

## 278 genotypes without replication
tab <- table(data$genotype[data$cross2015=="cross"&!is.na(data$cross)&!is.na(data$QPCR)])
length(tab[tab==1])

## Extract BLUPS
coefqPCR <- m1$coefficient$random[grepl("genotype",names(m1$coefficient$random))&m1$coefficient$random!=0]
## Extract genotype, pop, year
coefqPCRname <- strsplit(names(coefqPCR),":")
coefqPCRname <- lapply(coefqPCRname,function(x){strsplit(x,"_")})

pop = do.call("rbind", lapply(coefqPCRname, "[[", 1))
geno = do.call("rbind", lapply(coefqPCRname, "[[", 2))

BLUPqPCR <- data.frame(pop[,3],geno[,2],coefqPCR)

names(BLUPqPCR) <- c("pop","geno","BLUP")
head(BLUPqPCR)

## 344 genotypes
BLUPqPCR$year <- as.factor(rep("2015",nrow(BLUPqPCR)))
nrow(BLUPqPCR[BLUPqPCR$year=="2015",])

BLUPqPCR$genotype_year <- paste(BLUPqPCR$geno,BLUPqPCR$year,sep="_")

BLUPqPCR$real <- BLUPqPCR$genotype_year%in%data$genotype_year

## Get rid of genotypes with infered BLUPS (i.e. that were not observed that year)
BLUPqPCR <- BLUPqPCR[BLUPqPCR$real==T,]
write.csv(BLUPqPCR,file="BLUPsqPCR2015.csv",row.names=F,quote=F)

```